GSS Education and Environment

### 2023-04-20 outputs/paper/paper.qmd
Final changes

The remainder of this paper has four sections. In section 2, we explain the data source and methodologies used for data collection, data cleaning, variables used, potential biases and ethical issues. In section 3, we present a logistic regression model, estimating the relationship between a respondent’s willingness to donate money, their education, and whether they actually donate money. In section 4, the final results and model is interpreted along with all findings regarding respondents’ willingness and respondents’ donation behaviour, in relation to their education level obtained. Finally, a discussion is carried out, providing the implications of this paper’s findings, as well as the weaknesses and future steps of this investigation.

@@

As we analyse across the range of degrees obtained by respondents in @fig-3, we see a consistency in that there are very few respondents who are very willing to pay for environmental protection. This aligns to the fact that environmental nonprofits raise far less in comparison to other types of nonprofits. There are several reasons that may explain this: donors are not being properly taught about how their money supports organisations and makes a difference, the public may receive conflicting information about the environment, the lack of easily understandable resources, and more. This therefore highlights the overall need for improved strategies to increase peoples’ willingness to care for and support environmental change.

@@

Although this paper provides valuable insight to the groups of respondents - respondents with high school as their highest education level - who require more support in translating their attitudes into action, as well as the overall lack of environmental action and behaviour across education levels, there are many weaknesses that need to be considered going forward. First, is it important to recognise that pay is not the only way that one can show their attitude towards the environment. Additionally, education is related to other factors including income. Thus, some respondents may have expressed that they would pay for environmental protection, but not have been able to due to financial factors. Some respondents may have not donated money to an environmental group in the past five years, but may have contributed positively to the environment through volunteer work, or making an effort to reduce their environmental impact. These scenarios and factors, and many others, are not considered in this paper, but should be investigated going forward in this area of research. Lastly, it may be interesting to conduct research to see how the trends and findings change with in-person data collection or overtime.

>>>>

The remainder of this paper has four sections. In section 2, we explain the data source and methodologies used for data collection, data cleaning, variables used, potential biases and ethical issues. In section 3, we present a logistic regression model, estimating the relationship between a respondent’s willingness to donate money, their education, and whether they actually donate money. In section 4, the final results are presented and interpreted. Finally, a discussion is carried out, providing the implications of this paper’s findings, as well as the weaknesses and future steps of this investigation.

@@

As we analyse across the range of degrees obtained by respondents in @fig-3, we see a consistency in that there are very few respondents who are very willing to pay for environmental protection. There are several reasons that may explain this: donors are not being properly taught about how their money supports organisations and makes a difference, the public may receive conflicting information about the environment, the lack of easily understandable resources, and more. This therefore highlights the overall need for improved strategies to increase peoples’ willingness to care for and support environmental change.

@@

Although this paper provides valuable insight to the groups of respondents - respondents with high school as their highest education level - who require more support in translating their attitudes into action, as well as the overall lack of environmental action and behaviour across all education levels, there are many weaknesses that need to be considered going forward. First, is it important to recognise that pay is not the only way that one can show their attitude towards the environment. Additionally, education is related to other factors including income. Thus, some respondents may have expressed that they would be willing to pay for environmental protection, but not have been able to due to financial factors. Some respondents may have not donated money to an environmental group in the past five years, but may have contributed positively to the environment through volunteer work, or making an effort to reduce their environmental impact. These scenarios and factors, and many others, are not considered in this paper, but should be investigated going forward in this area of research. Lastly, it may be interesting to conduct research to see how the trends and findings change with in-person data collection or overtime.
